### 2016-07-15 filters-notions.tex
cheers

In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.  In the top notion, the hash functions are secret.  This is the setting addressed by NY, and it captures applications in which the hash functions are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions
public, but assumes that the adversary only accesses them in a
black-box manner.  That is, the adversary does not exploit
structural features of the hash functions in its attack.  This
notion makes it easy to track the query complexity of an attack, and
also allows us to capture constructions in the random-oracle model.
\tsnote{This is the setting for the Neidermayer et al.\  attacks.
It's also the setting for ROM attacks.} \jnote{I don't think the
middle notion is interesting. I disagree regarding the attacks of
Neidermayer et al.: there, the hash functions are secret (though
they are based on public ``random oracles'' $g$ and $h$). The ROM
can be handled separately by giving all algorithms access to
the~RO.}

>>>>

In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.  In the top notion, the hash functions are secret.  This is the setting addressed by NY, and it captures applications in which the hash functions are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.
%
The bottom notion considers the case that the full code of the hash functions is known to the attacker.  This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
%
The middle notion is a compromise: it makes the hash functions
public, but assumes that the adversary only accesses them in a
black-box manner.  That is, the adversary does not exploit
structural features of the hash functions in its attack.  This
notion makes it easy to track the query complexity of an attack, and
also allows us to capture constructions in the random-oracle model.
\tsnote{This is the setting for the Neidermayer et al.\  attacks.
It's also the setting for ROM attacks.} \jnote{I don't think the
middle notion is interesting. I disagree regarding the attacks of
Neidermayer et al.: there, the hash functions are secret (though
they are based on public ``random oracles'' $g$ and $h$). The ROM
can be handled separately by giving all algorithms access to
the~RO.}\tsnote{You're correct; I misread some of the text.  It is
only the setup for the attack that needs access to the hash functions,
and this is just modeling what is likely to appear in the real
``encrypted'' BFs.}
